---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# pfrscrapr

<!-- badges: start -->
<!-- badges: end -->

The pfrscrapr package is a set of functions that _politely_ scrapes Pro Football Reference IDs and other data from PFR index pages.

A dependency is RSelenium. [You can learn about how to set up RSelenium here](https://www.youtube.com/watch?v=GnpJujF9dBw&t=10s).

Currently the function expects a Selenium server to be running locally on your machine on port 4445. In the future I would like to update the code to accommodate spinning up a Selenium server on demand.

## Installation

You can install the development version of pfrscrapr from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("friscojosh/pfrscrapr")
```

## Examples

You can scrape the NFL Season By Season Passing page

``` {r example_data}
library(pfrscrapr)
passing <- get_league_passing_by_year()
```


You can load all IDs

``` {r example}

pfrscrapr::load_ids()
```


You can get the PFR ID for a single player by converting their name to all 
lowercase and removing punctuation and suffixes:

```{r example1}
pfrscrapr::scrape_player_id("joe montana")
```

Or you can get the IDs of all players with a surname beginning with a letter:

```{r example2}
pfrscrapr::scrape_pfr_player_ids_by_letter("A")
```


Finally you can scrape all IDs and other data. This takes a long time -- at least three minutes. The total number of requests to PFR is low however: just 26, one for each letter in the alphabet. The rest of the time is spent running regular expressions. This scape also gives the positions each player has played, which is useful for matching.

```{r example4}
# do not run
# pfrscrapr::get_pfr_ids()
```
